---
title: "R Visualisation"
---

Imagine the following scenario:
You are a data analyst/scientist at an organisation. You have been given a data set and asked to create a meaningful data visualisation using this data.

Using the ggplot in-built data sets in RStudio and the qplot function, get your creative juices flowing and create a meaningful and impactful data visualization using your preferred data set.
----------------------
Ggplot data sets 
Use diamonds dataset →Prices of over 50,000 round cut diamonds
A dataset containing the prices and other attributes of almost 54,000 diamonds. The variables are as follows:

Format
A data frame with 53940 rows and 10 variables:

price
price in US dollars ($326--$18,823)

carat
weight of the diamond (0.2--5.01)

cut
quality of the cut (Fair, Good, Very Good, Premium, Ideal)

color
diamond colour, from D (best) to J (worst)

clarity
a measurement of how clear the diamond is (I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best))

x
length in mm (0--10.74)

y
width in mm (0--58.9)

z
depth in mm (0--31.8)

depth
total depth percentage = z / mean(x, y) = 2 * z / (x + y) (43--79)

table
width of top of diamond relative to widest point (43--95)
-------------
Examine dataset
```{r}
library(ggplot2)
head(diamonds)
```
Plot relationship between price and clarity of diamonds.

```{r}
#load library
library(ggplot2)
#Plot price vs diamond clarity
qplot(data = diamonds, x=price, geom = "histogram",
      main = "Clarity of Diamonds", fill = clarity)
```


Plot relationship between price and carat
------------------------------------------
```{r}
viz <- ggplot(data=diamonds, aes(x=price, y=carat)) +
       geom_point(aes(color=carat), alpha=.5) +
       geom_smooth()+
       labs(title="Diamond Price vs Carat", subtitle="Diamond Dataset from GGplot", x="Price ($)", y="weight of the diamond (Carat)", color = "Carat")
# Prints the plot
viz
```

Histogram of diamond carat
Majority of diamond has carat less 1.

```{r}
diamonds_histogram_binwidth <- 
  ggplot(diamonds, aes(x = carat)) + 
  labs(title = "Diamond Carat") +
  geom_histogram(binwidth = 0.1)
diamonds_histogram_binwidth
```


```{r}
diamonds_histogram_cut <- 
  ggplot(diamonds, aes(x = depth)) + 
  labs(title = "Diamond Depth") +
  geom_histogram()
diamonds_histogram_cut
```

Heatmap

Majority of diamond are color G with Ideal cut.

```{r}
diamond_heatmap <- 
  ggplot(diamonds,
         aes(x = color,
             y = cut)) +
  geom_bin2d()

diamond_heatmap
```

Boxplot
----------
carat
weight of the diamond (0.2--5.01)
clarity
a measurement of how clear the diamond is (I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best))

```{r}
diamond_boxplot <- 
  ggplot(diamonds, 
         aes(x = clarity, y = carat))  +
  geom_boxplot()

diamond_boxplot
```

Diamond with best clarity tends to have smaller weight than diamond with worst clarity (I1)
-----------------
Stacked Bar Plots
-----------------
shows the ratios of diamond clarity between the different cuts.

```{r}
diamond_stackedbar_fill <- 
  ggplot(diamonds, 
         aes(x = cut, 
             y = price, 
             fill = clarity)) + 
  geom_col(position = "fill")

diamond_stackedbar_fill
```

Ideal cut has the highest percentage of IF clarity (the best).
-----------


```{r}
diamond_clusteredbar <- 
  ggplot(diamonds, 
         aes(x = cut, 
             y = price, 
             fill = clarity)) +
  geom_col(position = "dodge")

diamond_clusteredbar
```


