
---
title: "Home Learning Task"

---

1. Write a R program to take input from the user (name and age) and display the values. 
```{r}
name = readline("Enter your name: ")
age = readline("Enter your age: ")
hello =  paste("Welcome",name,"! Your age is ", age,"!")
print(hello)
```

2. Write a R program to get the details of the objects in memory. Hint: how do you list all the local variables?

```{r}
ls()
```

3. Write a R program to create a sequence of numbers from 20 to 50 and find the mean of numbers from 20 to 60 and sum of numbers from 51 to 91.

```{r}
print("Sequence of numbers from 20 to 50:")
print(seq(20,50))
print("Mean of numbers from 20 to 60:")
print(mean(20:60))
print("Sum of numbers from 51 to 91:")
print(sum(51:91))
```

4. Write a R program to create a vector which contains 10 random integer values between -50 and +50

```{r}
v = sample(-50:50, 10, replace=TRUE)
print("Content of the vector:")
print("10 random integer values between -50 and +50:")
print(v)
```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

