---
title: "Home Learning Task"
---

1. Write an R program to create three vectors a, b, c with 5 integers. Combine the three vectors to become a 3×5 matrix where each column represents a vector. Print the content of the matrix. Plot a graph and label correctly.

```{r}
a<-c(1,2,3,4,5)
b<-c(6,7,8,9,10)
c<-c(11,12,13,14,15)
m<-cbind(a,b,c)
print("Content of the said matrix:")
print(m)
```

```{r}
table <-cbind(a,b,c)
print(table)
#plots a graph
matplot(table, type = "b", pch=15:15, col=1:3)
```

2. Write a R program to create a Data frames which contain details of 5 employees and display the details. (Name, Age, Gender, Role and Length of service).

```{r}
Employees = data.frame(Name=c("Anastasia S","Dima R","Katherine S", "JAMES A","LAURA MARTIN"),
                  Age=c(23,22,25,26,32),                      
                  Gender=c("M","M","F","F","M"),
                  Role=c("Clerk","Manager","Exective","CEO","ASSISTANT"),
                  Length_of_service=c("12","5","6","20","3")
                      )
print("Details of the employees:")                      
print(Employees)
```

Import the GGPLOT 2 library and plot a graph using the qplot function. X axis is the sequence of 1:20 and the y axis is the x ^ 2. Label the graph appropriately. install.packages("ggplot2", dependencies = TRUE)

```{r}
library(ggplot2)
?diamonds
cont <- data.frame(y=c(x^2), x=1:20)
ggplot(data=cont, aes(x=x, y=y)) + geom_point()
#qplot(data = diamonds, x=price, geom = "histogram",
#      main = "Clarity of Diamonds", fill = clarity)
```



4. Create a simple bar plot of five subjects

```{r}
marks = c(70, 95, 80, 74)
barplot(marks,
main = "Comparing marks of 5 subjects",
xlab = "Marks",
ylab = "Subject",
names.arg = c("English", "Science", "Math.", "Hist."),
col = "darkred",
horiz = FALSE)
```

---
title: "Challenge"
---
1. Write a R program to get the first 10 Fibonacci numbers.

```{r}
Fibonacci <- numeric(10)
Fibonacci[1] <- Fibonacci[2] <- 1
for (i in 3:10) Fibonacci[i] <- Fibonacci[i - 2] + Fibonacci[i - 1]
print("First 10 Fibonacci numbers:")
print(Fibonacci)
```

2. Write a R program to print the numbers from 1 to 100 and print "Fizz" for multiples of 3, print "Buzz" for multiples of 5, and print "FizzBuzz" for multiples of both.


```{r}
for (n in 1:100) {
 if (n %% 3 == 0 & n %% 5 == 0) {print("FizzBuzz")}
 else if (n %% 3 == 0) {print("Fizz")}
 else if (n %% 5 == 0) {print("Buzz")}
 else print(n)
}
```


